Annotated metamodel for MSR course papers

### 2015-08-06 presentations/paper/paper.tex
Fix my own English in abstract

\begin{abstract}
  In 2014, Git surpassed Subversion as the top code management tool
  \cite{EComSurv14}. With many authors collaborating comes the need for an
  appropriate and standardized use of elemental actions, like formulating
  commit messages. Although the official Git documentation states very clear
  guidelines \cite{OffGuide} on how this should be done, maby of users are not
  aware of them or simply ignore them.

>>>>

\begin{abstract}
  In 2014, Git surpassed Subversion as the top code management tool
  \cite{EComSurv14}. With many authors collaborating comes the need for an
  appropriate and standardized use of elemental actions, like formulating
  commit messages. Although the official Git documentation states very clear
  guidelines \cite{OffGuide} on how this should be done, many users are either
  unaware or simply ignore them.
